Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-03-06 manuscript/manuscript.Rmd
new figures

Figures
-------
```{r figure_1, dependson="plot-options", fig.cap="Boxplots of model residuals for one-step-ahead forecasts at each observation year for each quadrat. Residuals represent the difference in observed and predicted cover change from year $t-1$ to year $t$. Each one-step forecast was simulated 100 times for each quadrat. Note that the y-axes vary across panels.", fig.width=8, fig.height=8, cache=FALSE, results='hide'}
resD <- readRDS("../montana/quadBM/simulations/oneStepResids_YearEffects.rds")
resDny <- readRDS("../montana/quadBM/simulations/oneStepResids_NoYearEffects.rds")
resD$simtype <- rep("full", nrow(resD))
resDny$simtype <- rep("noyear", nrow(resDny))
resDall <- rbind(resD, resDny)
noZ <- which(resDall$lagCover!=0)
resDall <- resDall[noZ,]

@@

# nSims <- length(unique(resD$sim))
# diffD <- ddply(resDall, c("year", "species", "simtype"), summarise,
#                avgDiff = median(resids, na.rm = TRUE),
#                upDiff75 = quantile(resids, probs = 0.8775, names=FALSE, na.rm = TRUE),
#                dnDiff75 = quantile(resids, probs = 0.1225, names=FALSE, na.rm = TRUE),
#                dnDiff95 = quantile(resids, probs = 0.025, names=FALSE, na.rm = TRUE),
#                upDiff95 = quantile(resids, probs = 0.975, names=FALSE, na.rm = TRUE))

# ggplot(diffD, aes(color=simtype))+
#   geom_hline(aes(yintercept=0), linetype=2, color="grey50")+
#   geom_point(aes(x=as.character(year), y=avgDiff), size=3, position=position_dodge(width=0.5))+
#   geom_errorbar(aes(x=as.character(year), ymax=upDiff95, ymin=dnDiff95), width=0.00001, position=position_dodge(width=0.5))+
#   geom_errorbar(aes(x=as.character(year), ymax=upDiff75, ymin=dnDiff75), size=1, width=0.00001, position=position_dodge(width=0.5))+
#   facet_grid(species~., scales = "free_y")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   scale_color_manual(values=myCols)+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
# 
# ggplot(resDall)+
#   geom_hline(aes(yintercept=0), linetype=2)+
# #   geom_line(data=diffD, aes(x=year, y=avgDiff, group=species), color="purple", alpha=0.5)+
# #   stat_smooth(data=diffD, aes(x=year, y=avgDiff, group=species), color="lightblue", se = FALSE, size=1)+
#   geom_boxplot(aes(x=year, y=resids, fill=simtype), outlier.shape = 1, width=0.3, outlier.size = 0.5)+
#   facet_grid(species~., scales = "free_y")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
# myCols <- c("#237DA4", "#7ECAD0")
p1 <- ggplot(subset(resDall, species=="BOGR"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  coord_cartesian(ylim = c(-50, 50))+
  ggtitle(expression(italic("B. gracilis")))+
  guides(fill=FALSE)
p2 <- ggplot(subset(resDall, species=="HECO"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols, labels=c("Year effects", "No year effects"))+
  ggtitle(expression(italic("H. comita")))+
  coord_cartesian(ylim = c(-10, 5))+
  guides(fill=guide_legend(title=""))+
  theme(legend.position=c(0.5,0.2))
p3 <- ggplot(subset(resDall, species=="PASM"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  ggtitle(expression(italic("P. smithii")))+
  guides(fill=FALSE)+
  coord_cartesian(ylim = c(-1.5, 1.5))
p4 <- ggplot(subset(resDall, species=="POSE"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  ggtitle(expression(italic("Poa secunda")))+
  guides(fill=FALSE)+
  coord_cartesian(ylim = c(-10, 15))
pFinal <- grid.arrange(p1,p2,p3,p4, ncol=2, nrow=2)
pFinal

```{r figure_2, dependson="plot-options", fig.cap="One step forecasts from IPM version.",fig.width=8, fig.height=8, cache=FALSE, results='hide'}
ipm_onestep <- readRDS("../montana/ipm/simulations/one_step_results/ipm_one-step_forecasts_combined.rds")
ipm_onestep$t1 <- ipm_onestep$t1+1900
p1 <- ggplot(subset(ipm_onestep, species=="BOGR"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  coord_cartesian(ylim = c(-50, 50))+
  ggtitle(expression(italic("B. gracilis")))+
  guides(fill=FALSE)
p2 <- ggplot(subset(ipm_onestep, species=="HECO"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols, labels=c("Year effects", "No year effects"))+
  ggtitle(expression(italic("H. comita")))+
  coord_cartesian(ylim = c(-10, 5))+
  guides(fill=guide_legend(title=""))+
  theme(legend.position=c(0.5,0.2))
p3 <- ggplot(subset(ipm_onestep, species=="PASM"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  ggtitle(expression(italic("P. smithii")))+
  guides(fill=FALSE)+
  coord_cartesian(ylim = c(-1.5, 1.5))
p4 <- ggplot(subset(ipm_onestep, species=="POSE"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  ggtitle(expression(italic("Poa secunda")))+
  guides(fill=FALSE)+
  coord_cartesian(ylim = c(-10, 15))
pFinal <- grid.arrange(p1,p2,p3,p4, ncol=2, nrow=2)
pFinal
```

```{r figure_3, dependson="plot-options", fig.cap="One step forecasts from IPM version.",fig.width=8, fig.height=8, cache=FALSE, results='hide'}
ipm_onestep2 <- subset(ipm_onestep, year=="ayear effect")
resDall2 <- subset(resDall, simtype=="full")
ipm_qbm_onestep <- data.frame(year = c(ipm_onestep2$t1, resDall2$year),
                              resids = c(ipm_onestep2$resid, resDall2$resids),
                              model = c(rep("IPM", nrow(ipm_onestep2)),
                                        rep("QBM", nrow(resDall2))),
                              species = c(ipm_onestep2$species, resDall2$species))
g1 <- ggplot(subset(ipm_qbm_onestep, species=="BOGR"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  coord_cartesian(ylim = c(-50, 50))+
  ggtitle(expression(italic("B. gracilis")))+
  guides(fill=FALSE)
g2 <- ggplot(subset(ipm_qbm_onestep, species=="HECO"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  coord_cartesian(ylim = c(-10, 5))+
  ggtitle(expression(italic("H. comata")))+
  guides(fill=guide_legend(title=""))+
  theme(legend.position=c(0.5,0.2))
g3 <- ggplot(subset(ipm_qbm_onestep, species=="PASM"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  ggtitle(expression(italic("P. smithii")))+
  guides(fill=FALSE)+
  coord_cartesian(ylim = c(-1.5, 1.5))
g4 <- ggplot(subset(ipm_qbm_onestep, species=="POSE"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  ggtitle(expression(italic("Poa secunda")))+
  coord_cartesian(ylim = c(-10, 15))+
  guides(fill=FALSE)
pFinal <- grid.arrange(g1,g2,g3,g4, ncol=2, nrow=2)
pFinal
```

>>>>

Figures
-------
```{r figure_1,cache=FALSE, results='hide'}
# resD <- readRDS("../montana/quadBM/simulations/oneStepResids_YearEffects.rds")
# resDny <- readRDS("../montana/quadBM/simulations/oneStepResids_NoYearEffects.rds")
# resD$simtype <- rep("full", nrow(resD))
# resDny$simtype <- rep("noyear", nrow(resDny))
# resDall <- rbind(resD, resDny)
# noZ <- which(resDall$lagCover!=0)
# resDall <- resDall[noZ,]
# 
# myCols <- c("#237DA4", "#7ECAD0")
# # ggplot(resDall, aes(x=resids, fill=simtype))+
# #   geom_histogram(alpha=0.5)+
# #   facet_grid(.~species, scales = "free_x")+
# #   xlab("Year")+
# #   ylab("Residuals (% cover difference)")+
# #   theme_bw()+
# #   scale_fill_manual(values=myCols)
# 
# resAgg <- ddply(resDall, .(year, species, simtype), summarise,
#                 avg_prediction = mean(cover)*100,
#                 up_prediction = quantile(cover, probs = 0.875)*100,
#                 down_prediction = quantile(cover, probs = 0.125)*100,
#                 avg_obs = mean(propCover)*100)
# resAgg$model <- rep("QBM", nrow(resAggipm))

# ggplot(subset(resAgg))+
#   geom_ribbon(aes(x=year, ymin=down_prediction, ymax=up_prediction, fill=simtype), alpha=0.3)+
#   geom_line(aes(x=year, y=avg_prediction, color=simtype), size=1.5)+
# #   geom_line(aes(x=year, y=up_prediction, color=simtype), linetype=2, alpha=0.5)+
# #   geom_line(aes(x=year, y=down_prediction, color=simtype), linetype=2, alpha=0.5)+
#   geom_point(aes(x=year, y=avg_obs), shape=1, size=3)+
#   facet_grid(species~., scales="free")+
#   scale_fill_manual(values=c(myCols[1], "darkorange"), labels=c("Year effects", "No year effects"))+
#   scale_color_manual(values=c(myCols[1], "darkorange"))+
#   guides(color=FALSE)
# nSims <- length(unique(resD$sim))
# diffD <- ddply(resDall, c("year", "species", "simtype"), summarise,
#                avgDiff = median(resids, na.rm = TRUE),
#                upDiff75 = quantile(resids, probs = 0.8775, names=FALSE, na.rm = TRUE),
#                dnDiff75 = quantile(resids, probs = 0.1225, names=FALSE, na.rm = TRUE),
#                dnDiff95 = quantile(resids, probs = 0.025, names=FALSE, na.rm = TRUE),
#                upDiff95 = quantile(resids, probs = 0.975, names=FALSE, na.rm = TRUE))

# ggplot(diffD, aes(color=simtype))+
#   geom_hline(aes(yintercept=0), linetype=2, color="grey50")+
#   geom_point(aes(x=as.character(year), y=avgDiff), size=3, position=position_dodge(width=0.5))+
#   geom_errorbar(aes(x=as.character(year), ymax=upDiff95, ymin=dnDiff95), width=0.00001, position=position_dodge(width=0.5))+
#   geom_errorbar(aes(x=as.character(year), ymax=upDiff75, ymin=dnDiff75), size=1, width=0.00001, position=position_dodge(width=0.5))+
#   facet_grid(species~., scales = "free_y")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   scale_color_manual(values=myCols)+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
# 
# ggplot(resDall)+
#   geom_hline(aes(yintercept=0), linetype=2)+
# #   geom_line(data=diffD, aes(x=year, y=avgDiff, group=species), color="purple", alpha=0.5)+
# #   stat_smooth(data=diffD, aes(x=year, y=avgDiff, group=species), color="lightblue", se = FALSE, size=1)+
#   geom_boxplot(aes(x=year, y=resids, fill=simtype), outlier.shape = 1, width=0.3, outlier.size = 0.5)+
#   facet_grid(species~., scales = "free_y")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
# myCols <- c("#237DA4", "#7ECAD0")
# p1 <- ggplot(subset(resDall, species=="BOGR"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   coord_cartesian(ylim = c(-50, 50))+
#   ggtitle(expression(italic("B. gracilis")))+
#   guides(fill=FALSE)
# p2 <- ggplot(subset(resDall, species=="HECO"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols, labels=c("Year effects", "No year effects"))+
#   ggtitle(expression(italic("H. comita")))+
#   coord_cartesian(ylim = c(-10, 5))+
#   guides(fill=guide_legend(title=""))+
#   theme(legend.position=c(0.5,0.2))
# p3 <- ggplot(subset(resDall, species=="PASM"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("P. smithii")))+
#   guides(fill=FALSE)+
#   coord_cartesian(ylim = c(-1.5, 1.5))
# p4 <- ggplot(subset(resDall, species=="POSE"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("Poa secunda")))+
#   guides(fill=FALSE)+
#   coord_cartesian(ylim = c(-10, 15))
# pFinal <- grid.arrange(p1,p2,p3,p4, ncol=2, nrow=2)
# pFinal

```{r figure_2, dependson="plot-options", fig.cap="One step forecasts from IPM version.",fig.width=8, fig.height=8, cache=FALSE, results='hide'}
resD <- readRDS("../montana/quadBM/simulations/oneStepResids_YearEffects.rds")
resDny <- readRDS("../montana/quadBM/simulations/oneStepResids_NoYearEffects.rds")
resD$simtype <- rep("full", nrow(resD))
resDny$simtype <- rep("noyear", nrow(resDny))
resDall <- rbind(resD, resDny)
noZ <- which(resDall$lagCover!=0)
resDall <- resDall[noZ,]

@@

resAgg <- ddply(resDall, .(year, species, simtype), summarise,
                avg_prediction = mean(cover)*100,
                up_prediction = quantile(cover, probs = 0.875)*100,
                down_prediction = quantile(cover, probs = 0.125)*100,
                avg_obs = mean(propCover)*100)
resAgg$model <- rep("QBM", nrow(resAgg))

ipm_onestep <- readRDS("../montana/ipm/simulations/one_step_results/ipm_one-step_forecasts_combined.rds")
ipm_onestep$t1 <- ipm_onestep$t1+1900

resAggipm <- ddply(ipm_onestep, .(t1, species, year), summarise,
                avg_prediction = mean(cover.t1)*100,
                up_prediction = quantile(cover.t1, probs = 0.875)*100,
                down_prediction = quantile(cover.t1, probs = 0.125)*100,
                avg_obs = mean(obs.cover.t1)*100)
colnames(resAggipm)[1:3] <- c("year", "species", "simtype")
resAggipm$simtype[which(resAggipm$simtype=="ayear effect")] <- "full"
resAggipm$simtype[which(resAggipm$simtype!="full")] <- "noyear"
resAggipm$model <- rep("IPM", nrow(resAggipm))

resAgg_both <- rbind(resAgg, resAggipm)

ggplot(subset(resAgg_both))+
  geom_ribbon(aes(x=year, ymin=down_prediction, ymax=up_prediction, fill=simtype), alpha=0.3)+
  geom_line(aes(x=year, y=avg_prediction, color=simtype), size=1.5)+
  geom_point(aes(x=year, y=avg_obs), shape=1, size=3)+
  facet_grid(species~model, scales="free")+
  scale_fill_manual(values=c(myCols[1], "darkorange"), labels=c("Year effects", "No year effects"))+
  scale_color_manual(values=c(myCols[1], "darkorange"))+
  guides(color=FALSE)

ggplot(subset(resAgg_both))+
  geom_ribbon(aes(x=year, ymin=down_prediction, ymax=up_prediction, fill=model), alpha=0.3)+
  geom_line(aes(x=year, y=avg_prediction, color=model), size=1.5)+
  geom_point(aes(x=year, y=avg_obs), shape=1, size=3)+
  facet_grid(species~simtype, scales="free")+
  scale_fill_manual(values=c(myCols[1], "darkorange"))+
  scale_color_manual(values=c(myCols[1], "darkorange"))+
  guides(color=FALSE)

# p1 <- ggplot(subset(ipm_onestep, species=="BOGR"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   coord_cartesian(ylim = c(-50, 50))+
#   ggtitle(expression(italic("B. gracilis")))+
#   guides(fill=FALSE)
# p2 <- ggplot(subset(ipm_onestep, species=="HECO"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols, labels=c("Year effects", "No year effects"))+
#   ggtitle(expression(italic("H. comita")))+
#   coord_cartesian(ylim = c(-10, 5))+
#   guides(fill=guide_legend(title=""))+
#   theme(legend.position=c(0.5,0.2))
# p3 <- ggplot(subset(ipm_onestep, species=="PASM"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("P. smithii")))+
#   guides(fill=FALSE)+
#   coord_cartesian(ylim = c(-1.5, 1.5))
# p4 <- ggplot(subset(ipm_onestep, species=="POSE"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("Poa secunda")))+
#   guides(fill=FALSE)+
#   coord_cartesian(ylim = c(-10, 15))
# pFinal <- grid.arrange(p1,p2,p3,p4, ncol=2, nrow=2)
# pFinal
```

```{r figure_3, dependson="plot-options", fig.cap="One step forecasts from IPM version.",fig.width=8, fig.height=8, cache=FALSE, results='hide', eval=FALSE}
ipm_onestep2 <- subset(ipm_onestep, year=="ayear effect")
resDall2 <- subset(resDall, simtype=="full")
ipm_qbm_onestep <- data.frame(year = c(ipm_onestep2$t1, resDall2$year),
                              resids = c(ipm_onestep2$resid, resDall2$resids),
                              model = c(rep("IPM", nrow(ipm_onestep2)),
                                        rep("QBM", nrow(resDall2))),
                              species = c(ipm_onestep2$species, resDall2$species))
g1 <- ggplot(subset(ipm_qbm_onestep, species=="BOGR"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  coord_cartesian(ylim = c(-50, 50))+
  ggtitle(expression(italic("B. gracilis")))+
  guides(fill=FALSE)
g2 <- ggplot(subset(ipm_qbm_onestep, species=="HECO"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  coord_cartesian(ylim = c(-10, 5))+
  ggtitle(expression(italic("H. comata")))+
  guides(fill=guide_legend(title=""))+
  theme(legend.position=c(0.5,0.2))
g3 <- ggplot(subset(ipm_qbm_onestep, species=="PASM"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  ggtitle(expression(italic("P. smithii")))+
  guides(fill=FALSE)+
  coord_cartesian(ylim = c(-1.5, 1.5))
g4 <- ggplot(subset(ipm_qbm_onestep, species=="POSE"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  ggtitle(expression(italic("Poa secunda")))+
  coord_cartesian(ylim = c(-10, 15))+
  guides(fill=FALSE)
pFinal <- grid.arrange(g1,g2,g3,g4, ncol=2, nrow=2)
pFinal
```
